High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-10-09 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

% Abstract of the paper
\begin{abstract}
    The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions. The ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.56\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au. In addition, central emission is detected close to the star which we interpret as a tight circumbinary ring made of dust grains with a lower size limit of 0.8\,mm at 1.1\,au. In order to reproduce the SED, the model also requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding the inner circumbinary disc. The surprisingly thin Ring13 is nonetheless roughly 10 times wider than its expected vertical extent. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
\end{abstract}

@@

A parametric model that simultaneously fits the NIR scattered light and millimetre continuum emission links the observations to the structures in the underlying dust and gas density distributions, and sheds light on the complex processes that shaped them. In this paper, we present \red{\sout{new}} ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr, which reveal an inner ring in the disc. We also reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the \red{\sout{new}} high definition 1.3\,mm continuum map. Section~\ref{sec:Observations} describes the available observations that we aim to model. Section~\ref{sec:model} describes the structural parameters of our model. A description of our parameter space exploration can be found in Appendix~\ref{sec:Appendix}. The results of our modelling are presented in Section~\ref{sec:results}, including a discussion of the main findings. Finally, in Section~\ref{sec:Conclusions} we present our conclusions.

@@

The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} reveals new substructure of the disc, in the form of two rings of large dust grains with a broad gap between them, i.e. Ring13 at $\sim$13\,au and Ring24 starting at $\sim$24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, continues relatively flat and then breaks at $\sim$35\,au into a steeper tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} anticipated its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}. We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{2021arXiv210408379C}, which minimises the dispersion of the intensity radial profiles \red{between two given radii. That way we take a range that fully includes Ring13 but not Ring24, so the range goes} from 6 to 18\,au for the first optimization. The resulting disc orientation is set at a position angle (PA) of 257.31$\pm$0.03\,deg (east of north), with an inclination of 147.04$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars. The offset of the center of the cavity and the nominal stellar positions are coincident within the pointing accuracy of ALMA, which  is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).

In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 256.86$\pm$0.02\,deg, with an inclination of 146.08$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing accuracy. However, see that there are some hints for a somewhat different orientation in the azimuthal profiles for the ring radii, which may nonetheless be accounted for by the joint effect of all these small differences in disc orientation. This is summarised in Fig.~\ref{fig:polarring}a, which characterises the radial position and width of Ring13 as a function of azimuth by using radial Gaussian fits at each azimuth. The radial centroids for both disc orientation overlap within the errors, but there is a systematic trend for the difference between the two. It may be that this small difference reflects a finite  intrinsic eccentricity of one or both rings. Deeper imaging is required to progress on this question.

@@

The scattered light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01\,au, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the near-far brightness asymmetry, and the shadows projected on the disc by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}. We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015} (see Fig.~\ref{fig:SED}). The SED exhibits the dip near 10\,$\micron$ characteristic of transition discs, as described by \citet{Rosenfeld_2013}. \citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.2\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.pdf}
    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the \red{resulting SED of radiative transfer model (solid blue line)}. The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

@@

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep[version 2.0,][]{Dullemond_2012}. The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}. A high-resolution radiative transfer model that reproduces multi-frequency imaging and the SED, is a solution to a highly degenerate problem, so a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper. Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data, and then, improve this fit by implementing one dimensional least squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}). The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel the surface density profiles for gas and dust grains populations, and in the lower panel the respective aspect ratio profile.

@@

The observed SED reveals a small near-infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}, this low emission would be primarily emanating from micron-sized dust grains at the hot inner dust wall of a low-mass inner disc. On the other hand, the mm-bright central emission suggests a massive inner dust ring. The faint near-IR excess contrast with the bright mm emission, and could point to a lack of micron-sized dust in the central ring, that could be due to efficient dust growth or due to the ring having an inner radius well beyond the sublimation radius. In order to reproduce the low NIR and simultaneous bright central mm emission, we extended the radius of an inner cavity to significantly exceed both the sublimation radius \red{\sout{($\sim$0.05\,au)}} and the zone that is expected to be cleared by dynamical binary-disc interaction \red{\sout{\citep[][$\lesssim$0.1\,au]{Art_Lu}} (see Appendix~\ref{sec:A2})}. A possible explanation for this wider cavity is the presence of an additional effect of truncation, like an unseen companion planet in the very inner part of the disc \citep{Francis_2020}. At the same time, the central emission is also well reproduced in the ALMA image with the inclusion of a Gaussian ring at 1.1\,au. This inner ring produces a low near-IR excess only if it consists of dust grains larger than $\sim$0.3\,mm (see Appendix.~\ref{sec:A1}). But we implement 0.8\,mm instead as the lower limit for the dust population that composes this feature, given that this predicts a dust mass of 0.012\,M$_{\earth}$, which is close to that obtained by \citet{Francis_2020} (0.013$\pm$0.002,M${\earth}$). They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0\red{, on the other hand, our mass estimations are made directly from the values extracted from the RT model. }
\begin{figure}
	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images. The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim$0$\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
    \label{fig:radprofiles}
\end{figure}

@@

\red{The expected age of >20\,Myr of V4046\,Sgr suggests that its gas-rich disc is unconventionally old in comparison to typical circumstellar examples \citep[e.g.][]{Fedele2010, Williams2011}. The dispersal of such gas discs is typically assumed to be set by photo-evaporation \citep{Alexander2006,Gorti2009}. While the dynamical origin of the disc's longevity is not subject of the study at hand, we would like to mention that its occurrence around such a close binary might not be coincidental. \citet{Alexander2012} predicted that disc lifetimes should show a sharp increase around binaries separated by $\lesssim 0.3-1.0\,$au. It still has to be seen whether a trend towards longer disc lifetimes in compact multiple-star systems (as recently proposed by \citealp{Ronco2021}) turns out to be prevalent.}

@@

\subsection{Parameter space partial exploration} \label{sec:A1}
As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of the parameter space.

@@

\red{The inner radius of the disc is usually defined by one of two phenomena, photo-evaporation or dynamical interaction with the central stars. The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{\mathrm{sub}}=0.07\sqrt{L_*(L_{\sun})}$,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}. On the other hand, \citet{Jensen_97} concluded from the SED that the system matched that of a disc truncated at $\sim$0.2\,au. For our model we have found that following the latter value gives a significant improvement in the SED fit (see Fig.~\ref{fig:SED_comparition}), therefore, the inner radius of the disc in our best-fitting model lies at 0.2\,au.}

\red{The final structure of our proposed disc also include some nontrivial features that were necessary in order to fit the SED and the images simultaneously. Those were the inner large-dust ring at 1.1\,au responsible for the central emission, and the thin Gaussian ring made mainly of small dust grains at 5.2\,au (Ring5). The first one is visible in the ALMA image so we are forced to include it, but Ring5 was added as its contribution to the SED is substantial.}

\red{Fig.~\ref{fig:SED_comparition} works as a summary as it shows a comparison between our best-fitting model and five models with changes on their structures: one without Ring5, one without the inner large-dust disc, one without both of those structures, another with an inner edge of the disc at 0.085\,au, and a last one with an inner edge of the disc at 0.05\,au. All these models drift away from the SED data somewhere in the 6-300\,$\micron$ range. This noticeable offset led us to propose the presented model structure, where we found that adding Ring5 and the inner large-dust ring, and setting the inner edge of the disc at 0.2\,au improved the SED fit considerably.}

\begin{figure*}
	\includegraphics[width=\columnwidth]{SED_three_model_comparision.pdf}
        \caption{\red{Side-to-side comparison between spectral energy distributions of our model versus five other models with differences in their dust structure. Every model drift away from the best-fitting SED somewhere between 6 and 300\,$\micron$. The figure shows the impact that removing or changing one of them would have on the SED. The dotted lines represent the models with different inner radius while the dashed lines represent the models without Ring5 or the inner large-dust disc.}}
        %the truncation radius due to dynamical binary-disc interaction.
    \label{fig:SED_comparition}

\end{figure*}

>>>>

% Abstract of the paper
\begin{abstract}
    The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present high resolution ($\sim$20\,mas or 1.4\,au) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions. The ALMA data reveal a thin ring at a radius of 13.15$\pm$0.42\,au (Ring13), with a radial width of 2.46$\pm$0.56\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. Between 25 and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steep tail that reaches out to $\sim$60\,au. In addition, central emission is detected close to the star which we interpret as a tight circumbinary ring made of dust grains with a lower size limit of 0.8\,mm at 1.1\,au. In order to reproduce the SED, the model also requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding the inner circumbinary disc. The surprisingly thin Ring13 is nonetheless roughly 10 times wider than its expected vertical extent. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
\end{abstract}

@@

A parametric model that simultaneously fits the NIR scattered light and millimetre continuum emission links the observations to the structures in the underlying dust and gas density distributions, and sheds light on the complex processes that shaped them. In this paper, we present new ALMA observations of the continuum emission at 1.3\,mm of V4046\,Sgr with unprecedented angular resolution in this source, which reveal an inner ring in the disc. We also reproduce these observations with a 3D parametric model that fits all available data, including the polarized scattered light SPHERE image, the spectral energy distribution (SED), as well as the \red{\sout{new}} high definition 1.3\,mm continuum map. Section~\ref{sec:Observations} describes the available observations that we aim to model. Section~\ref{sec:model} describes the structural parameters of our model. A description of our parameter space exploration can be found in Appendix~\ref{sec:Appendix}. The results of our modelling are presented in Section~\ref{sec:results}, including a discussion of the main findings. Finally, in Section~\ref{sec:Conclusions} we present our conclusions.

@@

The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} reveals new substructure of the disc, in the form of two rings of large dust grains with a broad gap between them, i.e. Ring13 at \red{$\sim$}13\,au and Ring24 starting at \red{$\sim$}24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, continues relatively flat and then breaks at $\sim$35\,au into a steeper tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} anticipated its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

Ring13 is surprisingly narrow and seems to be off-centred relative to the Gaia stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}. We determined the ring's centre and orientation using the {\tt MPolarMaps} package described in \citep{10.1093/mnras/stab2359}, which minimises the dispersion of the intensity radial profiles \red{between two given radii. In an initial optimization we focus on the orientation of Ring13, and choose a radial range from from 6 to 18\,au, which covers Ring13 but excludes Ring24.} The resulting disc orientation is set at a position angle (PA) of 257.31$\pm$0.03\,deg (east of north), with an inclination of 147.04$\pm$0.02\,deg, and the optimal ring centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the Gaia position of the stars. The offset of the center of the cavity and the nominal stellar positions are coincident within the pointing accuracy of ALMA, which  is $\sim$5\,mas for the signal to noise ratio of our image (calculated using the ALMA Technical Handbook).

In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au \red{(fully including Ring24 and excluding Ring13)}, we obtained a PA of 256.86$\pm$0.02\,deg, with an inclination of 146.08$\pm$0.01\,deg and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors and the pointing accuracy. However, see that there are some hints for a somewhat different orientation in the azimuthal profiles for the ring radii, which may nonetheless be accounted for by the joint effect of all these small differences in disc orientation. This is summarised in Fig.~\ref{fig:polarring}a, which characterises the radial position and width of Ring13 as a function of azimuth by using radial Gaussian fits at each azimuth. The radial centroids for both disc orientation overlap within the errors, but there is a systematic trend for the difference between the two. It may be that this small difference reflects a finite  intrinsic eccentricity of one or both rings. Deeper imaging is required to progress on this question.

@@

The scattered light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01\,au, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au \red{\citep{Ru_z_Rodr_guez_2019}}. Two other important features that are present in the image are: the near-far brightness asymmetry, and the shadows projected on the disc by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}. We also used archival \textit{Spitzer} IRS spectroscopic data available in the CASSIS database \citep{Lebouteiller_2015}. \red{The data is displayed in Fig.~\ref{fig:SED} along with the resulting SED of the radiative transfer model presented in the next section (more on the SED in Sec.~\ref{sec:results})}. The SED exhibits the dip near 10\,$\micron$ characteristic of transition discs, as described by \citet{Rosenfeld_2013}. \citet{Jensen_97} concluded that these data matched that of a extended circumbinary disc truncated at $\sim$0.2\,au, as the interior would also be expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.pdf}
    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the \red{model SED resulting from the RT model (solid blue line)}. The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

@@

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep[version 2.0,][]{Dullemond_2012}. The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}. A high-resolution radiative transfer model that reproduces multi-frequency imaging and the SED, is a solution to a highly degenerate problem, so a full parameter exploration requires a level of computation and time that exceeds our capabilities and the scope of this paper. Consequently, our approach was to find through trial and error a set of values for the 3parameters that closely fit the available data, and then, improve this fit by implementing one dimensional least squared optimizations for some key parameters (more on this in Sec.~\ref{sec:results}). The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel the surface density profiles for gas and dust grains populations, and in the lower panel the respective aspect ratio profile.

@@

The observed SED reveals a small near-infrared (NIR) excess of 0.9$\pm$3.7\,\% \citep{Francis_2020}, this low emission would be primarily emanating from micron-sized dust grains at the hot inner dust wall of a low-mass inner disc. On the other hand, the mm-bright central emission suggests a massive inner dust ring. The faint near-IR excess contrast with the bright mm emission, and could point to a lack of micron-sized dust in the central ring, that could be due to efficient dust growth or due to the ring having an inner radius well beyond the sublimation radius. In order to reproduce the low NIR and simultaneous bright central mm emission, we extended the radius of an inner cavity to significantly exceed both the sublimation radius \red{\sout{($\sim$0.05\,au)}} and the zone that is expected to be cleared by dynamical binary-disc interaction \red{\sout{\citep[][$\lesssim$0.1\,au]{Art_Lu}} (see Appendix~\ref{sec:A2})}. A possible explanation for this wider cavity is the presence of an additional effect of truncation, like an unseen companion planet in the very inner part of the disc \citep{Francis_2020}. At the same time, the central emission is also well reproduced in the ALMA image with the inclusion of a Gaussian ring at 1.1\,au. This inner ring produces a low near-IR excess only if it consists of dust grains larger than $\sim$0.3\,mm (see Appendix.~\ref{sec:A1}). But we implement 0.8\,mm instead as the lower limit for the dust population that composes this feature, given that this predicts a dust mass of 0.012\,M$_{\earth}$, which is close to that obtained by \citet{Francis_2020} (0.013$\pm$0.002,M${\earth}$). They converted mm-flux into mass using the standard opacity value of $\kappa_{\nu}$=10\,$\mathrm{cm}^2 \mathrm{g}^{-1}$ at 1000\,GHz with an opacity power-law index of $\beta$=1.0\red{, while our mass estimates are  extracted from the RT model.}
\begin{figure}
	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images. The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim$0$\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
    \label{fig:radprofiles}
\end{figure}

@@

\red{The expected age of >20\,Myr of V4046\,Sgr suggests that its gas-rich disc is unconventionally old in comparison to typical circumstellar examples \citep[e.g.][]{Fedele2010, Williams2011}. The dispersal of such gas discs is typically assumed to be set by photo-evaporation \citep{Alexander2006,Gorti2009}. While the dynamical origin of the disc’s longevity is not the subject of the present study, we would like to mention that its occurrence around such a close binary might not be coincidental. \citet{Alexander2012} predicted that disc lifetimes should show a sharp increase around binaries separated by $\lesssim 0.3-1.0\,$au. It still has to be seen whether a trend towards longer disc lifetimes in compact multiple-star systems (as recently proposed by \citealp{Ronco2021}) turns out to be prevalent.}

@@

\subsection{Parameter space partial exploration} \label{sec:A1}

As a way to compute a measure of goodness of fit and to try to quantify the model uncertainties, we performed a partial exploration of the parameter space.

@@

\red{A compact inner hole in the dust distribution around a binary can typically be produced by sublimation of solids or dynamical clearing of the central stars. The sublimation radius of the system is expected to be at $\sim$0.05\,au \citep[$R_{\mathrm{sub}}=0.07\sqrt{L_*(L_{\sun})}$\,au,][]{Francis_2020}, and the edge of the zone cleared by dynamical interactions between the near-circular binary and the circumbinary disc is estimated to be at 0.085\,au \citep[$r=2.08a$,][]{Art_Lu}. On the other hand, for V4046 Sgr, \citet{Jensen_97} required to implement a cavity to 0.2\,au to fit the SED flux around the silicate feature at 10\,$\micron$. We find that the latter value significantly improves the SED fit when compared to a disc extending to the inner radius predicted by dynamical clearing in the SED fit (see Fig.~\ref{fig:SED_comparition}), therefore, the inner radius of the disc in our best-fitting model lies at 0.2\,au.}

\red{The final structure of our proposed disc also includes additional features that are necessary to fit both the SED and the images. These features are a cut-off of the inner density accumulation of large dust grains outside of 1.1\,au (to fit the central emission in the ALMA image), and the thin Gaussian ring made mainly of small dust grains at 5.2\,au (Ring5, demanded by mid-infrared excess in the SED). The first one is visible in the ALMA image so we are forced to include it, but Ring5 is not detected in the ALMA continuum and was included because of its contribution to the 10$\micron$ flux is required by the SED. Fig.~\ref{fig:SED_comparition} works as a summary as it shows a comparison between our best-fitting model and five models with changes on their structures: one without Ring5, one without the inner large-dust disc, one without both of those structures, another with an inner edge of the disc at 0.085\,au, and a last one with an inner edge of the disc at 0.05\,au. All these models diverge from the SED data somewhere in the 6-300\,$\micron$ range.}

\begin{figure}
	\includegraphics[width=\columnwidth]{SED_three_model_comparision.pdf}
        \caption{\red{Comparison between the SEDs of best-fitting model versus five other models with differences in the dust structure. The dotted lines represent the models with different inner radius while the dashed lines represent the models without Ring5 or the inner large-dust disc.}}
        %the truncation radius due to dynamical binary-disc interaction.
    \label{fig:SED_comparition}

\end{figure}
